Races with hyper3 objects

### 2022-06-28 inst/race3.Rmd
point to constructor_names.txt

Looking at the first column we see that the constructors are Mercedes
("`Merc`"), Red Bull Racing Honda ("`RBRH`"), and so on.  Each
constructor fields two cars in each race.  Looking at the next column,
we see the order statistic for Bahrain (`BHR`).  We see that Mercedes
came first and third, Red Bull came second and fifth, Ferrari sixth
and eighth, and so on.

>>>>

Looking at the first column we see that the constructors are Mercedes
("`Merc`"), Red Bull Racing Honda ("`RBRH`"), and so on (see file
`inst/constructor_names.txt` for a list of abbreviations).  Each
constructor fields two cars in each race.  Looking at the next column,
we see the order statistic for Bahrain (`BHR`).  We see that Mercedes
came first and third, Red Bull came second and fifth, Ferrari sixth
and eighth, and so on.
